A formal approach but practical approach in train regulation

### 2025-06-17 paper/main.tex
minor corrections

\newcommand{\directions}{{\mathsf{D}}}
\newcommand{\turnouts}{{\mathsf{\theta}}}
\newcommand{\blocks}{{\mathsf{B}}}
\newcommand{\internalState}{{\mathcal{I}}}
\newcommand{\forward}{{\mathtt{f}}}
\newcommand{\backward}{{\mathtt{b}}}
\newcommand{\sucblock}{{\mathtt{suc}}}

@@

Now, we come to the train model. Each train has an identifier. Without loss of generality, the identifiers form a set  $\trains = \{1, \ldots, k\}$. Each train has a position on the network. The position is the index of the block it stays in or the last block it left. Next, a train has a direction in $\directions$. The direction does not mean the train is running---it can be blocked by some red signal---but that its next move will be in that direction. Finally, a train has orders. Orders are given as a sequence of orders following the grammar:
$$  seq ::= \su(dir,pos) $$
with $dir \in \directions$ and $pos \in \blocks$. An order $\su(d, pid)$ states that the train direction is set to $d$ and that the train runs until it reaches $pid$.  The sequence may be empty.

To sum up, trains can be viewed as 4-tuples: $t = (id, pos, dir, P)$ with $id$ the train's identifier, $pos$ its position, $dir$ its direction and $P$ the sequence of orders. The description of all trains is then a sequence $\Gamma = (t_1, \ldots, t_k)$ with $t_1$ the 4-tuple corresponding to train 1, up to $t_k$ that is the 4-tuple corresponding to train $k$.

>>>>

\newcommand{\directions}{{\mathsf{D}}}
\newcommand{\turnouts}{{\mathsf{\theta}}}
\newcommand{\blocks}{{\mathsf{B}}}
\newcommand{\internalState}{{\mathcal{I}}}
\newcommand{\forward}{{\mathtt{f}}}
\newcommand{\backward}{{\mathtt{b}}}
\newcommand{\idle}{{\mathtt{*}}}
\newcommand{\sucblock}{{\mathtt{suc}}}

@@

Now, we come to the train model. Each train has an identifier. Without loss of generality, the identifiers form a set  $\trains = \{1, \ldots, k\}$. Each train has a position on the network. The position is the index of the block it stays in or the last block it left. Next, a train has a direction in $\{\forward, \backward, \idle\}$ with $\idle$ meaning idle status.  The direction does not mean the train is running---it can be blocked by some red signal---but that its next move will be in that direction. Finally, a train has orders. Orders are given as a sequence of orders following the grammar:
$$  seq ::= \su(d,pid) $$
with $d \in \directions$ and $pid \in \blocks$. An order $\su(d, pid)$ states that the train direction must be set to $d$ and that the train runs until it reaches $pid$.  The sequence may be empty.

To sum up, trains can be viewed as 4-tuples: $t = (tid, pid, d, P)$ with $tid$ the train's identifier, $pid$ its position, $d$ its direction and $P$ the sequence of orders. The description of all trains is then a sequence $\Gamma = (t_1, \ldots, t_k)$ with $t_1$ the 4-tuple corresponding to train 1, up to $t_k$ that is the 4-tuple corresponding to train $k$.
